Metropolitan Areas (Deaths & Case)

### 2020-11-11 KPMG Team/Dashboard/visualization_scripts/msa_areas_map.Rmd
cities area

```{r}
### ----- SET DATE RANGE FIRST ----- ## 
```

@@

# --------------------------------------# 
# without filtering (run this)
census_msa <- census_msa_merge
# ------------------------------------ #
names(nyt)

county_sum <- nyt %>% 
  group_by(county, state, fips) %>%
  summarise(cases_sum = sum(cases, na.rm = TRUE))

@@

# final count of msa cases, in order to get ranking
msa_covid_sum <- msa_covid %>% 
  group_by(msa, msa_title, msa_population) %>%
  mutate(cases = sum(cases)) %>% 
  mutate(deaths = sum(deaths)) %>%
  arrange(desc(cases)) %>% 
  select(msa, msa_title, msa_population, cases, deaths) %>% 
  distinct() %>% # remove repeated values 
  na.omit()
  # drop_na(msa) # remove rows with NA in msa column

@@

# states in Texas 
plot_usmap(include = .midwest_region, labels = TRUE)

# get FIPS codes (state + county)
# fips(state = "CA", county = "Orange")

# FIPS county codes to Lat Long
geoFips <- function() {

@@

ggplot(data = county_map_US) +
  geom_sf(aes(fill = cases_sum)) + 
  scale_fill_viridis_c(option = "magma", direction = 1)

@@

ggplot(data = county_map_NY) +
  geom_sf(aes(fill = cases_sum)) + 
  scale_fill_viridis_c(option = "magma", direction = -1)

names(county_map_US)

fips(state = "New York")

table(c(county_map_US$statefp, county_map_US$state))

@@

  ggplot(data = county_map_state) +
  geom_sf(aes(fill = cases_sum)) + 
  scale_fill_viridis_c(option = "magma", direction = -1)

@@

>>>>

city <- read_csv("cities.csv")

View(city)
```

@@

# --------------------------------------# 
# without filtering (run this)
census_msa <- census_msa_merge

# ------------------------------------ #
names(nyt)

county_sum <- nyt %>%
  filter(date == max(nyt$date)) # latest

@@

# final count of msa cases, in order to get ranking
msa_covid_sum <- msa_covid %>% 
  group_by(msa, msa_title, msa_population) %>%
  mutate(total_cases = sum(new_cases)) %>% 
  mutate(total_deaths = sum(new_deaths)) #%>%
  arrange(desc(total_cases)) %>% 
  select(msa, msa_title, msa_population, total_cases, total_deaths) %>% 
  distinct() %>% # remove repeated values 
  na.omit()
  # drop_na(msa) # remove rows with NA in msa column

msa_covid_sum <- msa_covid %>% 
  filter(date == max(msa_covid$date)) %>% 
  select(msa, msa_title, msa_population, date, cases_sum, deaths_sum) #%>% 
  # distinct() #%>%
  # drop_na(msa)

View(msa_covid_sum)

table(msa_covid$msa_title)

@@

@@

ggplot(data = county_map_US) +
  geom_sf(aes(fill = cases)) + 
  scale_fill_viridis_c(option = "magma", direction = 1)

@@

# # plot for states 
# ggplot(data = county_map_NY) +
#   geom_sf(aes(fill = cases)) + 
#   scale_fill_viridis_c(option = "magma", direction = -1) +
# 
# 
# names(county_map_US)
# 
# fips(state = "New York")

@@

  ggplot(data = county_map_state) +
  geom_sf(aes(fill = cases)) + 
  scale_fill_viridis_c(option = "magma", direction = -1)

@@

range(county_map_US$cases)
